Demystifying the Computer Science \\ PhD Admission in the US\\{\large A Handbook for International \emph{and Domestic} Students

### 2024-04-07 demystify.tex
updates

In contrast, \emph{teaching} (or instructional faculty or professor of practice) mainly focuses on teaching. They typically teach 3--4 classes per semester (which is quite a lot) and \emph{do not} have research responsibilities, e.g., they do not have to worry much about publishing papers or obtaining grants. They can mentor PhD students but they typically cannot serve as a formal adviser of PhD students, i.e., they \emph{cannot graduate} PhD students.

@@

Adjunct faculty is not full-time, e.g., they might be working in industry and teach a class or two for fun.  Emeritus means they are retired but still have some affiliation with the university.  Research faculty (or research scientists) are typically non-tenure line faculty who focus on research.  Due to their roles, adjunct, emeritus, and research faculty typically do not advise PhD students.

>>>>

In contrast, \emph{teaching} (sometimes called instructional faculty or professor of practice) mainly focuses on teaching. They typically teach 3--4 classes per semester (which is quite a lot) and \emph{do not} have research responsibilities, e.g., they do not have to worry much about publishing papers or obtaining grants. As such they typically do not have funding (e.g., RA~\autoref{sec:funding}) to support PhD students.
Depends on the university, they might be able to \emph{co-advise} and mentor PhD students with a tenure-line faculty.

@@

Adjunct faculty is not full-time, e.g., they might be working in industry and teach a class or two for fun.  Emeritus means they are retired but still have some affiliation with the university.   Due to their roles, adjunct, emeritus, and research faculty typically do not advise PhD students.

\emph{Research faculty} or research scientists are typically non-tenure line faculty who focus on research. While they cannot serve as a formal adviser, they often co-advise and mentor students with tenure-line faculty. They can recruit students and provide RA funding for them as they typically have their own funding.
